---
output: github_document
---

# Repo for the paper "A note on joint calibration estimators for totals and quantiles"

The working paper is available [here](paper/beresewicz-szymkowiak-jointcalib.pdf).

## Preliminaries

Install `jointCalib` package

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("ncn-foreigners/jointCalib")
remotes::install_github("ncn-foreigners/nonprobsvy") ## for IPW with calibration constraints
```

Then, restart R  and load the package

```{r}
library(jointCalib)
library(nonprobsvy)
```

## Notebooks

1. [Main simulation from the paper](https://htmlpreview.github.io/?https://raw.githubusercontent.com/ncn-foreigners/paper-note-joint-calibration/main/notebooks/sim-chen2020-jasa-modif-results.html) based on Chen, Y., Li, P., and Wu, C. (2020). *Doubly robust inference with nonprobability survey samples*. Journal of the American Statistical Association, 115(532):2011–2021
2. [Tutorial for the `jointCalib` package](https://github.com/ncn-foreigners/jointCalib)
3. [A minimal example of joint calibration in R, Python and stata](https://htmlpreview.github.io/?https://raw.githubusercontent.com/ncn-foreigners/paper-note-joint-calibration/main/notebooks/qcalib-r-python-stata.html)

## Structure of the repo

+ `codes/` -- code for simulation
+ `figs/` -- figures that correspondst to table in the paper
+ `notebooks/` -- notebooks with processing results
+ `paper/` -- folder with the paper
+ `results/` -- files with tables based on simulation

## Funding

Work on this paper is supported by the the National Science Center, OPUS 22 grant no. 2020/39/B/HS4/00941.

